\vskip -20 pt CrypTool-Skript\footnote{Hintergrundmaterial und Zusatzinformationen zum Programm CrypTool} \\ Mathematik und Kryptographie

### 2003-06-13 script/de/chapters/digitalsignatures.tex
be updates

\bibitem[Schneier1996]{5Schneier1996ds} \index{Schneier 1996} 
    Bruce Schneier, \\
    Applied Cryptography, Protocols, Algorithms, and Source Code in C, \\
    Wiley, 2nd edition, 1996.

\bibitem[PKCS1]{PKCS1} RSA Laboratories\\ 
    \index{PKCS\#1} \index{RSA Laboratories}
    PKCS \#1 v2.1 Draft 3: RSA Cryptography Standard, April 19, 2002.

\bibitem[X.509v3]{X.509v3} ITU-T\\ 
    \index{X.509} \index{ITU-T} \index{ISO/IEC 9594-8}
    X.509 (1993) Amendment 1: Certificate Extensions, The Directory
    Authentication Framework,\\ 
    International Telecommunication Union, Geneva, Switzerland, July 1995\\
    (equivalent to Amendment 1 to ISO/IEC 9594-8).

\bibitem[FIPS180-2]{FIPS180-2} U.S. Department of Commerce/N.I.S.T. 
    \index{FIPS180-2} \\
    Secure Hash Standard (SHS), August 1, 2002.\\
    (FIPS 180-2 will supersede FIPS 180-1 beginning February 1, 2003.)

\bibitem[FIPS186]{FIPS186} U.S. Department of Commerce/N.I.S.T. 
    \index{FIPS186} \\
    Entity authentication using public key cryptography, February 18, 1997.\\
    Nicht mehr g"ultig.

\bibitem[FIPS186-2]{FIPS186-2} U.S. Department of Commerce/N.I.S.T. 
    \index{FIPS186-2} \\
    Digital Signature Standard (DSS), January 27, 2000.\\
    Change Note: October 5, 2001.\\
    http://csrc.nist.gov/publications/fips/fips186-2/fips186-2-change1.pdf
\bibitem[X.509]{X.509}
    \index{X.509}
    ITU-T Recommendation X.509 (1997 E): Information Technology -- 
    Open Systems Interconnection -- The Directory: Authentication Framework, June 1997.

>>>>

\bibitem[Schneier1996]{5Schneier1996ds} \index{Schneier 1996} 
    Bruce Schneier, \\
    {\em Applied Cryptography, Protocols, Algorithms, and Source Code in C}, \\
    Wiley, 2nd edition, 1996.

\bibitem[PKCS1]{PKCS1} RSA Laboratories\\ 
    \index{PKCS\#1} \index{RSA Laboratories}
    {\em PKCS \#1 v2.1 Draft 3: RSA Cryptography Standard}, April 19, 2002.

\bibitem[X.509v3]{X.509v3} ITU-T\\ 
    \index{X.509} \index{ITU-T} \index{ISO/IEC 9594-8}
    {\em X.509 (1993) Amendment 1: Certificate Extensions, The Directory
    Authentication Framework},\\ 
    International Telecommunication Union, Geneva, Switzerland, July 1995\\
    (equivalent to Amendment 1 to ISO/IEC 9594-8).

\bibitem[FIPS180-2]{FIPS180-2} U.S. Department of Commerce/N.I.S.T. 
    \index{FIPS180-2} \\
    {\em Secure Hash Standard (SHS)}, August 1, 2002.\\
    (FIPS 180-2 will supersede FIPS 180-1 beginning February 1, 2003.)

\bibitem[FIPS186]{FIPS186} U.S. Department of Commerce/N.I.S.T. 
    \index{FIPS186} \\
    {\em Entity authentication using public key cryptography}, February 18, 1997.\\
    Nicht mehr g"ultig.

\bibitem[FIPS186-2]{FIPS186-2} U.S. Department of Commerce/N.I.S.T. 
    \index{FIPS186-2} \\
    {\em Digital Signature Standard (DSS)}, January 27, 2000.\\
    Change Note: October 5, 2001.\\
    http://csrc.nist.gov/publications/fips/fips186-2/fips186-2-change1.pdf
\bibitem[X.509]{X.509}
    \index{X.509}
    {\em ITU-T Recommendation X.509 (1997 E): Information Technology -- 
    Open Systems Interconnection -- The Directory: Authentication Framework}, June 1997.
